The MolSSI \qca Project: An open-source platform to compute, organize, and share quantum chemistry data

### 2020-05-18 response2.tex
Adjusted response to include new changes. -TDC

\noindent \textit{We have updated Figure 10 to provide a more complete visualization of the application.}

>>>>

\begin{itemize}
\item \textit{We updated Figure 10 to provide a more complete visualization of the application.}
\item \textit{We updated literature references to NWCHem, Psi4, and
  GAMESS on pp. 10-11.}
\item \textit{We made a minor change to Fig. 1 by switching "MQCS" to "MQCAS".}
\end{itemize}
